---
title: "Vignette for fars functions"
author: "JLYJ"
date: "6 dec 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This vignette serves to illustrate how to use the farsfunctions package. The farsfunctions package, contains geodata for car accidents for each state in the US for the years 2013-2015. 

Load packages
```{r load, echo = FALSE}
library(dplyr, quietly = T)
library(tidyr, quietly = T)
library(farsfunctions, quietly = T)
```
fars_map_state() is the main function of the package, and it visualizes accidents The function takes two arguments, state number and year.

> fars_map_state(state.num = 44, year = 2013)

```{r map, echo = FALSE}
devtools::document()
setwd(system.file("inst/extdata/", package = "farsfunctions"))
fars_map_state(state.num = 44, year = 2013)
```

Another useful function in the package is fars_summarize_years, which given a list of years, generates a summary table of the accidents for each month for the given years.

> fars_summarize_years(c(2014,2015))

```{r summarize, echo = FALSE}
setwd(system.file("./inst/extdata/", package = "farsfunctions"))
fars_summarize_years(c(2013,2014))
```


In addition to the main functions, a couple of helper functions are also included in the package.
fars_read_years also takes a list of years and returns data for the given years (Not shown)

> fars_read_years(c(2013,2014))

```{r read years, echo = FALSE}
setwd(system.file("./inst/extdata/", package = "farsfunctions"))
fars_read_years(c(2013,2014))
```

Two other small functions are make_filename which takes a year as input, and returns the corresponding filename+incl. path, and fars_read, which given a filename reads the coresponding data into memory.

> make_filename(2013) 

> fars_read()


```{r filename}
setwd(system.file("inst/extdata/", package = "farsfunctions"))
make_filename(2013)
fars_read("accident_2013.csv.bz2")
```



